### 2025-07-16 multiple-regression.qmd
20250716 - beta regression

```{r}
library("petersenlab")
library("rms")
library("car")
library("caret")
library("lme4")
library("performance")
library("lavaan")
library("mice")
library("miceadds")
library("interactions")
library("brms")
library("robustbase")
library("ordinal")
library("MASS")
library("broom")
library("effectsize")
library("tidymodels")
library("tidyverse")
library("knitr")
```

@@

betaRegression <- brms::brm(
  formula = target_share ~ age + height + weight,
  data = newdata %>% filter(position %in% c("WR")),
  family = zero_one_inflated_beta(),
)
```

>>>>

```{r}
library("petersenlab")
library("rms")
library("car")
library("caret")
library("lme4")
library("performance")
library("lavaan")
library("mice")
library("miceadds")
library("interactions")
library("brms")
library("parallelly")
library("robustbase")
library("ordinal")
library("MASS")
library("broom")
library("effectsize")
library("tidymodels")
library("tidyverse")
library("knitr")
```

@@

betaRegression <- brms::brm(
  formula = target_share ~ age + height + weight,
  data = newdata %>% filter(position %in% c("WR")),
  family = zero_one_inflated_beta(),
  cores = 4,
  threads = threading(parallelly::availableCores()),
  seed = 52242,
  silent = 0
)
```
